Imposing a Weight Norm Constraint for Neuro-Adaptive Control

### 2025-06-09 presentation/presentation.tex
ppt update

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Block options: Default, Alert, Example
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Extra packages for the demo:
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{ragged2e}
\usepackage{schemabloc}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\usepackage{calc}

\usepackage{svg}
\usepackage{media9}             %pdflatex, latex+dvips+ps2pdf, xelatex
\usepackage{multimedia}
\usepackage{animate}

% Title page details: 
\title{
    Imposing a Weight Norm Constraint for Neuro-Adaptive Control 
} 
\subtitle{
    \textit{IEEE European Control Conference (ECC) 2025}\\
}
\author{
  \textbf{Myeongseok Ryu}\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}
  }
\date{\today}
% \institute[short]{\inst{1} First \samelineand \inst{2} Second \samelineand \inst{3} Third}
\newcommand{\samelineand}{\\}
\institute{%
    \begin{minipage}[c]{\linewidth}
        \centering
        \inst{1}%
        Department of Mechanical and Robotics Engineering\\
        Gwangju Institute of Science and Technology
        \and
        \inst{2}%
        AI Graduate School\\
        Gwangju Institute of Science and Technology
  \end{minipage}
}
% make institute font size smaller
\setbeamerfont{institute}{size=\normalsize}

\logo{
  \vspace{-.7cm}%
  \includegraphics[height=0.3cm]{assets/kaist_logo.png}
  \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.jpg}
  \hspace{.6cm}%
  }

@@

\titlegraphic{logo_KAIST.png}

@@

@@

@@

@@

@@

\begin{frame}{\insertsubsectionhead}{Original Control Problem}
  \textbf{Objectives}:
  \begin{itemize}
    \item Minimize the tracking error by adapting the NN weights $\estwth$.
    \item Guarantee the stability of the system and the NN weights $\estwth$.
  \end{itemize}

  \begin{figure}
    \includegraphics[width=0.5\textwidth]{figures/problem.drawio.pdf}
    % \includesvg{figures/problem.drawio}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
  \end{figure}

  \let\thefootnote\relax\footnote{
    \textit{Notations}: 
      $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector, $\mv{\tau}$: Control input, $\mv{q}$: Joint position, $\estwth$: Estimated NN weights.
      }

@@

\begin{frame}{\insertsubsectionhead}{Equvalent Constrained Optimization Problem}

\begin{frame}{\insertsubsectionhead}{Inequality Constraint for Weight Boundedness}

@@

\begin{frame}{\insertsubsectionhead}{Steepest Descent Method}

\end{frame}
\subsection{Stability Analysis}

@@

@@

  % \animategraphics[loop,width=4cm]{gifs/overall-}
  \animategraphics[loop,width=4cm]{10}{gifs/overall-}{0}{10}

@@

  Flux theme comes with three pre-defined block style collections.\\
  % Native style (default) available as \verb+\setblockstyle{native}+\\[0.5cm]

  \centering
	\begin{minipage}[b]{0.5\textwidth}

	  \begin{block}{Default}
        Block content.
      \end{block}

      \begin{alertblock}{Alert}
        Block content.
      \end{alertblock}

      \begin{exampleblock}{Example}
        Block content.
      \end{exampleblock}

	\end{minipage}
\end{frame}

>>>>

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Block options: block, alertblock, exampleblock
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Extra packages for the demo:
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{ragged2e}
\usepackage{schemabloc}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% \usepackage{calc}
% \usepackage{svg}
% \usepackage{media9}             %pdflatex, latex+dvips+ps2pdf, xelatex
% \usepackage{multimedia}
% \usepackage{animate}

% Title page details: 
\title{
    Imposing a Weight Norm Constraint for Neuro-Adaptive Control 
} 
\subtitle{
    \textit{IEEE European Control Conference (ECC) 2025}\\
}
\author{
  \textbf{Myeongseok Ryu}\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}
  }
\date{2025-06-25}
\institute{%
    \begin{minipage}[c]{\linewidth}
        \centering
        \inst{1}%
        Department of Mechanical and Robotics Engineering\\
        Gwangju Institute of Science and Technology
        \and
        \inst{2}%
        AI Graduate School\\
        Gwangju Institute of Science and Technology
  \end{minipage}
}
\titlegraphic{assets/MIC_Lab_logo_white.png}
% make institute font size smaller
\setbeamerfont{institute}{size=\normalsize}

\logo{
  \vspace{-.7cm}%
  \includegraphics[height=0.3cm]{assets/kaist_logo.png}
  \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.png}
  \hspace{.6cm}%
  }

@@

@@

\begin{figure}
  \label{fig:general_framework}
  \includegraphics[width=0.65\textwidth]{figures/conv_nac.drawio.pdf}
  \caption{General framework of neuro-adaptive control (NAC).}
\end{figure}

@@

\begin{frame}{\insertsubsectionhead}{Boundedness of NN Weights}

@@

\begin{frame}{\insertsubsectionhead}{Input Saturation}

  The input saturation is generally handled using an auxiliary system.

  \begin{enumerate}
    \begin{columns}[T,onlytextwidth]
        \column{0.49\textwidth}
          \item \textbf{Auxiliary Systems}

      \begin{columns}[T,onlytextwidth]
        \column{0.49\textwidth}
          \item \textbf{Second?}

@@

\subsection{Architecture of the Proposed Method}

    \column{0.5\textwidth}

      \textbf{Target 2-link Robotic Manipulator System}:
      \begin{itemize}
        \item Control input saturation function $\mysat(\cdot)$.
        \item Desired trajectory $\mv{q}_d$ is given.
      \end{itemize}
        \begin{equation}
          \mm{M}\ddq + \mm{V}_m\dq + \mv{F} + \mv{G} + \mv{\tau}_d
          =
          \mysat(\mv{\tau})
        \end{equation}

      \textbf{Control Input}:
      \begin{itemize}
        \item NN's output $\mv{\Phi}$ is used as the control input.
        \item Consists of the estimated NN weights $\estwth$.
      \end{itemize}
      \begin{equation}
        \mv{\tau} := \mv{\Phi}(\mv{q}_n; \estwth)
      \end{equation}

      \textbf{Deep Neural Network (DNN)}:
      \begin{itemize}
        \item $k$ layers with $\estwth_i:=\myvec(\estwV_i)$.
        \item Activation function: $\phi(\cdot):=tanh(\cdot)$.
        \begin{equation}
          \mv{\Phi}(\mv{q}_n; \estwth)
          :=
          \begin{cases}
              \estwV_i^\top \act_i(\estNN_{i-1}), 
              &
              i\in\{1,\dots ,k\},
              \\
              \estwV_0^\top {\q}_n,
              &
              i=0
              ,
          \end{cases}
        \end{equation}
      \end{itemize}

    \column{0.5\textwidth}

      \begin{figure}
        \includegraphics[width=0.8\textwidth]{figures/Controller.drawio.pdf}
        \caption{Architecture of the proposed method.}
      \end{figure}

      \begin{figure}
        \includegraphics[width=0.7\textwidth]{figures/DNN.drawio.pdf}
        \caption{Architecture of the DNN.}
      \end{figure}

    \let\thefootnote\relax\footnote{
      \textit{Notations}: 
        $\mv{q}\in\R^n$: Joint position, $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector, $\mv{\tau}$: Control input, $\estwth$: Estimated NN weights.
        $\estwth$: Estimated NN weights, $\mv{e}$: Tracking error, $\mv{\tau}_d$: Disturbance, $\mysat(\cdot)$: Saturation function.
      }

@@

\begin{frame}{\insertsubsectionhead}{Optimization Problem}

  \column{0.45\textwidth}

    \textbf{Optimization Problem Statement}:

    \begin{itemize}
      \item \textbf{Find} NN weights $\estwth$,
      \item That \textbf{minimize} objective function $J(\cdot)$,
        \begin{equation}
          J(\mv{r}) := \frac{1}{2} \mv{r}^\top \mv{r}.
        \end{equation}
        \begin{itemize}
          \item where $\mv{r} := \ddt\mv{e} + \Lambda\mv{e}$ is the filtered tracking error,
        \end{itemize}
      \item while satisfying the following \textbf{constraints}:
        \begin{itemize}
          \item Boundedness of the NN weights $\estwth$.
          \item Saturation of the control input $\mv{\tau}$.
        \end{itemize}
    \end{itemize}

  \column{0.5\textwidth}

    \begin{block}{Considered Constraints}

      \begin{itemize}
        \item \textbf{Weight Boundedness}: 
          \begin{equation}
            c_{\theta_i}
            :=
            \norm{\estwth_i}^2 - \bar{\theta_i}^2 \le 0
            , 
            \forall i\in\{0,\ldots,k\}
          \end{equation}

        \item \textbf{Control Input Saturation}: 
          \begin{itemize}
            \item Input bound constraint:
            \begin{equation}
              c_{\overline{\tau}_i}
              :=
              \tau_i - \overline{\tau_i}
              \le 
              0
              ,
              c_{\underline{\tau}_i}
              :=
              \underline{\tau_i} - \tau_i
              \le 
              0
            \end{equation}
            \item Input norm constraint:
            \begin{equation}
              c_{\mv{\tau}}
              :=
              \norm{\mv{\tau}}^2 - \overline{\tau}^2
              \le
              0
            \end{equation}
        \end{itemize}
      \end{itemize}

    \end{block}

  \let\thefootnote\relax\footnote{
    \textit{Notations}: 
    $\Lambda\in\R_{>0}^{n\times n}$: filtering matrix
  }

@@

\begin{frame}{\insertsubsectionhead}{Optimization Problem}

    \column{0.5\textwidth}

      \centering
      \begin{minipage}{0.9\textwidth}%
        \begin{block}{Optimization Problem}%

          \begin{equation}
            \begin{matrix}
              \min_{\estwth} J(\mv{r};\estwth)
              \\\ \\
              \text{s.t. } c_{j}(\estwth) 
              \le 
              0
              ,
              \forall j\in\mathcal{J}
            \end{matrix}
          \end{equation}

        \end{block}
      \end{minipage}

    \column{0.5\textwidth}

      \centering
      \begin{minipage}{0.9\textwidth}%
        \begin{block}{MinMax Problem}%

          \begin{equation}
            \begin{matrix}
              \min_{\estwth}\max_{[\lambda_j]_{j\in\mathcal{J}}} L(\cdot)
              \\\ \\
              \text{where }
              L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{J}})
              :=
              J(\mv{r};\estwth)
              +
              \sum_{j\in\mathcal{J}} \lambda_j c_j(\estwth)
            \end{matrix}
          \end{equation}

        \end{block}
      \end{minipage}

@@

\begin{frame}{\insertsubsectionhead}{Steepest Descent/Ascent Method}

    \column{0.5\textwidth}

      \begin{minipage}{0.9\textwidth}%
        For the min/max problem, the steepest descent/ascent method is used to derive the adaptation law.
      \end{minipage}

      \vspace{0.5cm}

      \begin{minipage}{0.9\textwidth}%
        \textbf{Steepest Descent Method for $\estwth$}:
        \begin{equation}
          \ddtt\estwth
          =
          -\alpha 
          \pptfrac{L}{\estwth}
        \end{equation}

        \textbf{Steepest Ascent Method for $\lambda_j$}:
        \begin{equation}
          \ddtt\lambda_j = 
        \end{equation}
      \end{minipage}

    \column{0.5\textwidth}

      \centering
        \begin{block}{Adaptation Law}%

        \begin{subequations}
            \begin{align}
                    \ddt {{\estwth}}
                    &
                    =
                    -\alpha 
                    \ppfrac{L}{{\estwth}}
                    =-\alpha 
                    \left(
                        \ppfrac{J}{{\estwth}}
                        +
                        \sum_{j\in\mathcal{I}}
                        \lambda_j 
                        \ppfrac{c_j}{\estwth}
                    \right),
                    \\
                    \ddt\lambda_j
                    & 
                    = 
                    \beta_j
                    \ppfrac{L}{\lambda_j} 
                    = 
                    \beta_j c_j ,
                    \quad\quad\quad\quad      \      
                    \forall j\in\mathcal I,
                    \\
                    \lambda_j 
                    & 
                    = 
                    \max(\lambda_j,0) ,
            \end{align}
        \end{subequations}

        \end{block}

\subsection{Stability Analysis}

@@

  \begin{block}{Theorem 1}
    For the dynamical system described in (1), the neuro-adaptive controller in (2) with the weight adaptation laws in (12) ensure the boundedness of the filtered error $\mv{r}$ and the weight estimate $\estwth$, under the control input constraints satisfying Assumption 1 and 2. This holds under the weight norm constraint (5).
  \end{block}

  \begin{exampleblock}{Assumption 1}
    The constraint functions $c_j(\estwth),\forall j\in\mathcal{I}$, are convex in the $\tau$-space and satisfy $c_j(\estwth)\le0$ and $c_j(\idealwth)\le0$.
  \end{exampleblock}

  \begin{exampleblock}{Assumption 2}
    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap. 12 Def. 12.1]{Nocedal:2006aa}.
  \end{exampleblock}

  Proof of Theorem 1 is omitted due to space limitations. The detailed proof can be found in \cite{}.

@@

  % \animategraphics[loop,width=4cm]{gifs/overall-}
  % \animategraphics[loop,width=4cm]{10}{gifs/overall-}{0}{10}

@@

  \textbf{Summary of Contributions}
  \begin{itemize}
    \item Proposed a novel constrained optimization-based neuro-adaptive control (CONAC) method.
    \item Adaptation laws are derived using constrained optimization method.
    \item The proposed method guarantees the stability of the system and the boundedness of the NN weights.
    \item Feasibility of the proposed method is validated through numerical simulations and real-time experiments.
  \end{itemize}

  \textbf{Future Work}
  \begin{itemize}
    \item Extend the proposed method to state constraints.
    \item Enhance the robustness and flexibility of the proposed method for various systems.
  \end{itemize}
